% Resume style adapted to friend template (Jake Gutierrez / sb2nov style)
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\usepackage{censor}
\usepackage{setspace}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins (kept tight and consistent with template)
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Slightly increase line height to reduce bottom whitespace and aid readability
\setstretch{1.03}

% Section heading formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-1pt}}}

\newcommand{\classesList}[4]{\item\small{{#1 #2 #3 #4 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small #1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small #1 & \textbf{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

% Projects without dates
\newcommand{\resumeProjectHeadingNoDates}[1]{\item\small #1 \vspace{-2pt}}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

% Slightly more generous item spacing to stretch to the bottom neatly
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=4pt, topsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% ---------------- Header ----------------
\begin{flushleft}
  % ---------- left column ----------
  \begin{minipage}[t]{0.60\textwidth}
    {\Huge\bfseries Theo Vernacchio}\\[-1pt]
    \normalsize Bristol, United Kingdom
  \end{minipage}%
  % ---------- right column ----------
  \hfill
  \begin{minipage}[t]{0.35\textwidth}
    \raggedleft
    \href{mailto:theo.vernacchio@gmail.com}{\underline{theo.vernacchio@gmail.com}}\\[-1pt]
    (+44)\;7847\;893451
  \end{minipage}
\end{flushleft}

\vspace{0.55\baselineskip}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Bristol}{Sep. 2024 -- May 2027}
      {BSc Economics}{Bristol, UK}
      \resumeItemListStart
        \resumeItem{\textbf{On track for First-Class Honours}.}
        \resumeItem{\textbf{Relevant modules:} Development Economics (\textbf{75\%}), Economic Data (\textbf{70\%}), Mathematics, Statistical Methods, Economics.}
        \resumeItem{Member, \textbf{Bristol Investment Fund}.}
      \resumeItemListEnd
    \resumeSubheading
      {Alleyn's School}{Sep. 2017 -- Jul. 2024}
      {Secondary School}{London, UK}
      \resumeItemListStart
        \resumeItem{\textbf{A Levels:} Mathematics, Economics, Geography: \textbf{AAA}}
        \resumeItem{\textbf{IGCSEs:} 10 subjects -- six \textbf{9}s, three \textbf{8}s}
        \resumeItem{\textbf{Captain, Fives 1st Team} -- \textbf{U18 National Fives Singles Finalist}; Tennis 1st Team.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hospitality (Seasonal)}{May -- Jul. 2025}
      {Waiter/Bartender}{London, UK}
      \resumeItemListStart
        \resumeItem{Delivered table service to \textbf{100+} guests at Royal Ascot.}
        \resumeItem{Managed a team of \textbf{8} at the Chelsea Flower Show corporate lounge.}
        \resumeItem{Hosted a VIP lounge for \textbf{50} guests at the Royal Albert Hall: managed a private box of 8.}
        \resumeItem{Led a team of \textbf{6} at a high-profile \textbf{3-day} wedding; praised as ``particularly phenomenal.''}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {J.P. Morgan}{} % virtual programme
      {Investment Banking Job Simulation (Forage)}{}
      \resumeItemListStart
        \resumeItem{Screened and prioritised M\&A targets against client strategic and financial criteria.}
        \resumeItem{Built a \textbf{DCF} with scenario analysis; adjusted for competitor bids and supply-chain disruption.}
        \resumeItem{Produced a \textbf{2-page} client brief summarising company profile and auction process.}
      \resumeItemListEnd
    \resumeSubheading
      {Royal Bank of Canada (RBC)}{Aug. 2025}
      {Insight Day}{London, UK}
      \resumeItemListStart
        \resumeItem{Shadowed traders on the London trading floor; contrasted human execution with \textbf{VWAP} algorithms for liquidity and pricing.}
        \resumeItem{Reviewed large corporate share buyback mechanics with the Head of European Equity Solutions; discussed tactics to minimise market impact and achieve best execution.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.00in, label={}]
  \small\item{
    \textbf{Programming}{: Python, JavaScript} \\
    \textbf{Data/Analysis}{: Excel} \\
    \textbf{Tools}{: RStudio} \\
    \textbf{Web}{: HTML, CSS}
  }
\end{itemize}
\vspace{-10pt}

%-----------ADDITIONAL-----------
\section{Additional}
{\small
\begin{itemize}[leftmargin=0.00in,label={},itemsep=4pt,topsep=2pt]
  \item \textbf{Charles Stanley}: Attended a wealth management insight day; supported fund management through research.
  \item \textbf{Online Course}: 2-day investment banking course covering valuation methods, financial modelling, and industry insights (former Head of European Equity Research at Barclays).
  \item \textbf{Publications}: Created \href{https://vernacch.io}{\underline{vernacch.io}} -- monthly micro \& macroeconomic analysis detailing portfolio development; delivered \textbf{8.5\%} monthly ROI.
  \item \textbf{Certificates}: LAMDA Grade 8 Distinction; SEQ Level 1 Swimming Assistant (Teaching).
  \item \textbf{Interests}: Self-taught piano \& guitar; Bristol Squash 3rd Team.
\end{itemize}
}

\end{document}
